I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-17 Paper/proofs.tex
update proof

		\begin{corollary}
			\label{cor1}
			$$\max(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \max(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \min(\hat{m}) + bias_n$$
			$$\min(n)=\sum_{m \in L, W_{m n}>0}W_{m n} \min(\hat{m}) + \sum_{m \in L, W_{m n}<0}W_{mn} \max(\hat{m}) + bias_n$$
		\end{corollary}

		Notice that for all $x$, either $S(x)=+1$ and 
		$(\min(x),\max(x))=(\min(x_s),\max(x_s))$, 
		or $S(x)=-1$ and $(\min(x),\max(x))=(-\max(x_s),-\min(x_s))$.
		In both case, these two bounds are found in Lemma \ref{lemma2},
		from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.

@@

		\paragraph{DeepPoly bounds}

		To prove that DeepPoly bounds are the same as the exact bounds computed above, 
		we show that even the box abstraction (which is easier) would reach the exact bounds.
		We proceed inductively, and prove the inductive step.
		The initialization is obvious as Box Abstraction/DeepPoly is always exact for the initialization layer.

@@

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $N_I$. In $N_I$, there is no compensating pair.
				\end{lemma}

@@

				\begin{lemma}\label{lem:subnetwork2}
					The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $N_J$.
				\end{lemma}

@@

				By definition, for any $b\in N_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.

@@

					For any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
					as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Theorem \ref{th1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
				\end{proof}

@@

				\begin{lemma}
					In the standard framework, both $N_I$ and $N_J$ are accurate in the sense that for any $b$ in $N_I$ or $N_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
				\end{lemma}

				\begin{proof}
					For $N_I$, it is because of no compensating as proved in the first section. For $N_J$, it is because all nodes are either opened or constants.
				\end{proof}

>>>>

		\begin{corollary}
			\label{cor1}
			$$\max(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \max(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \min(\hat{b}) + \boldsymbol{bias}_c$$
			$$\min(c)=\sum_{b \in L, W_{bc}>0}W_{bc} \min(\hat{b}) + \sum_{b \in L, W_{bc}<0}W_{bc} \max(\hat{b}) + \boldsymbol{bias}_c$$
		\end{corollary}

		Notice that for all $x$, for both $S(c)=1$ or $S(c)=-1$, these two bounds are found in Lemma \ref{lemma2},
		from configuration $\boldsymbol{x}^*$ and $\boldsymbol{x}^\sharp$.

@@

		\paragraph{Approximation Bounds}

		To prove that Approximation Bounds are the same as the exact bounds computed above, 
		we show that even the box abstraction (which is easier) would reach the exact bounds.
		We proceed inductively, and prove the inductive step.
		The initialization is obvious as Box Abstraction/DeepPoly is always exact for the initialization layer.

@@

				\begin{lemma}\label{lem:subnetwork}
					$B_{pure}$ and $I$ can form a sub-network: every node in $B_{pure}\cup I$ only depends on nodes in $B_{pure}\cup I$ backward: if $c$ is in $B_{pure}\cup I$ but $b$ is not, then $W_{bc}=0$. We call this sub-network $D_I$. In $D_I$, there is no compensating pair.
				\end{lemma}

@@

				\begin{lemma}\label{lem:subnetwork2}
					The input set $J$ with nodes that only depends on $J$ forms a sub-network. This network contains all nodes that $S$ is not defined on them. We call this sub-network $D_J$.
				\end{lemma}

@@

				By definition, for any $b\in D_J$, either $b\in B_{open}$, or $b$ is a constant node: to it, any path from any input node must have zero weight.

@@

					For any fixed input vector $\boldsymbol{x}^0_J$, we can regard $\Val_{\boldsymbol{x}_I,\boldsymbol{x}^0_J}(z)$ as a DNN $D'$ with input nodes $a_i\in I$, with all $\boldsymbol{x}^0_J$ %and their propagation in hidden layers 
					as bias. In the simplified $D'$, there is no compensating path because of the definition of $I$. Therefore we can apply Lemma \ref{lem:key1} to get that $\Val_{x_I,\boldsymbol{x}^0_J}(z)$ reaches its maximal value for $\boldsymbol{x}_I=\boldsymbol{x}_I^*$, and we are done.
				\end{proof}

@@

				\begin{lemma}
					In the standard framework, both $D_I$ and $D_J$ are accurate in the sense that for any $b$ in $D_I$ or $D_J$, $\UB(b)=\max\Val(b)$ and $\LB(b)=\min\Val(b)$.
				\end{lemma}

				\begin{proof}
					For $D_I$, it is because of no compensating as proved in the first section. For $D_J$, it is because all nodes are either opened or constants.
				\end{proof}
